Energy and exergy analysis of a cruise ship

### 2017-06-04 Manuscript/Manuscript.tex
Modifications to headers file and manuscript

>>>>

Since measurements of ambient and seawater temperature from onboard logging systems were not available for the whole dataset, we used measurements taken from SMHI database for Landsort lighthouse. The assumption was validated using for the June-December period, for which onboard measurements were available. This resulted in a root mean square error of 1.5 K and 1.9 K for the seawater and the ambient temperature respectively, which we considered to be accurate enough for the purpose of this work.
% We did the calculation, resampling the data from SHMI from a 1(3)h to 15min frequency using linear interpolation.
